On the properties of discs around accreting brown dwarfs

### 2010-05-19 BD_disc/paper.tex
New figure
git-svn-id: https://repository.astro.ex.ac.uk/torus/trunk@2276 25464f21-6099-402c-b30a-640f1d40d38b

The density of material in the disc falls with increasing radius from
the star ($\rho\propto R_*^{\alpha}$). The dust sublimation
temperature is also density dependent \citep{pollack_1994}.
Therefore, for systems where the inner edge has been eroded
significantly from the co-rotation radius the temperature of the inner
edge will fall as the final radius increases. In this case a
correlation of inner edge temperature and inner edge radius is
expected with a resulting slope determined, at least in part, by the
radial density distribution of the disc. In this case the the final
inner edge radius and therefore temperature is no longer strongly
correlated with the rotation rate. Figure \ref{inner_temp} shows the
final inner edge location ($R_{\rm inner}$, $R_*$) against the
temperature of the inner wall ($T_{\rm inner}$, K). The \textit{left
  panel} shows the systems designated as typical accretors and the
\textit{right panel} those with extreme accretion rates. For
\textit{both panels} the systems with rotation periods of 0.5 and 5
days are plotted in red and blue respectively. Those systems where the
change in inner radius was greater than 1$R_*$, and therefore classes
as significantly sublimated, are plotted as crosses. These systems are
only present for the extreme accretors, as shown in Figure
\ref{delta_radius}. Furthermore, for the typical accretors Figure
\ref{delta_radius} shows that only the shorter period objects, in
general, experience any disc erosion at the inner edge.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/inner_temp.ps"
     hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
 \caption{Figure showing data for the inner edge location ($R_{\rm
     inner}$, $R_*$). The typical accretors are shown in the
   \textit{left panel} and the extreme accretors in the \textit{right
     panel} (see text for explanation). In \textit{both panels}
   separate the systems by period, with those systems with rotation
   periods of 0.5 and 5 days shown as red and blue symbols
   respectively. In addition systems where the total change in the
   inner radius is greater than 1$R_*$ are marked as crosses (this is
   only achieved by some systems classed as extreme
   accretors).\label{inner_temp}}
\end{figure*}

>>>>

The density of material in the disc falls with increasing radius from
the star ($\rho\propto R_*^{\alpha}$).  The dust sublimation
temperature is also density dependent \citep{pollack_1994}.
Therefore, for systems where the inner edge has been eroded
significantly from the co-rotation radius the temperature of the inner
edge will fall as the final radius increases.  In this case a
correlation of inner edge temperature and inner edge radius is
expected with a resulting slope determined, at least in part, by the
radial density distribution of the disc.  In this case the the final
inner edge radius and therefore temperature is no longer strongly
correlated with the rotation rate. Figure \ref{inner_temp} shows the
final inner edge location ($R_{\rm inner}$, $R_*$) against the
temperature of the inner wall ($T_{\rm inner}$, K). The \textit{left
  panel} shows the systems designated as typical accretors and the
\textit{right panel} those with extreme accretion rates.  For
\textit{both panels} the systems with rotation periods of 0.5 and 5
days are plotted in red and blue respectively. Systems where $\Delta
R_{\rm inner} < 1R_*$ are plotted ia crosses and $\Delta R_{\rm inner}
> 1R_*$ as filled circles, with the latter denoting systems with
significant sublimation. Significant sublimation is only found for the
extreme accretors, as shown in Figure \ref{delta_radius}.
Furthermore, for the typical accretors Figure \ref{delta_radius} shows
that only the shorter period objects, in general, experience any disc
erosion at the inner edge.

\begin{figure*}
  \vspace*{348pt}
  \special{psfile="Fig/inner_temp.ps"
     hoffset=470 voffset=0 hscale=60 vscale=60 angle=90}
   \caption{Figure showing data for the inner edge location ($R_{\rm
       inner}$, $R_*$). The typical accretors are shown in the
     \textit{left panel} and the extreme accretors in the
     \textit{right panel} (see text for explanation). In \textit{both
       panels} separate the systems by period, with those systems with
     rotation periods of 0.5 and 5 days shown as red and blue symbols
     respectively. In addition, systems where $\Delta R_{\rm inner} <
     1R_*$ are plotted ia crosses and $\Delta R_{\rm inner} > 1R_*$ as
     filled circles (this is only achieved by some systems classed as
     extreme accretors).\label{inner_temp}}
\end{figure*}
